---
title: "CA 21: Correlation"
output:
  html_document:
    css: ./style.css
    toc: yes
    toc_float: yes
    theme: cosmo
  pdf_document:
    toc: yes
editor_options:
  chunk_output_type: console
---

```{r global_options, include = FALSE}
library(knitr)
library(tidyverse)
knitr::opts_chunk$set(eval = TRUE, results = TRUE)
```

---

## Correlation

For the following section we will use data from: "Learning Statistics with R" by Danielle Navarro:

```{r}
load("~/MAT104-Fall2024/Week12/parenthood.Rdata")
load("~/MAT104-Fall2024/Week12pearson_correlations.RData")
load("~/MAT104-Fall2024/Week12/effort.Rdata")
```

+ This data captures how grumpy Danielle is, how much she slept in a day, and how much her baby slept in a day.

Consider the following plots:

```{r}
ggplot(parenthood, aes(x=dan.sleep, y=dan.grump)) + geom_point()
```

```{r}
ggplot(parenthood, aes(x=baby.sleep, y=dan.grump)) + geom_point()
```


### Correlation coefficient

The Pearson correlation coefficient $r_{XY}$ is a standardized covariance measure:

$$r_{XY} = \frac{1}{N-1} \sum_{i=1}^{N}
\frac{X_i-\bar{X}}{s_X}\frac{Y_i-\bar{Y}}{s_Y} $$

where $s_x$ and $s_y$ are the sample standard deviations. 

The R code for the Pearson correlation coefficient is:


### Properties of $r_{XY}$



### Interpreting the Pearson correlation coefficient

Below is data with various Pearson correlation coefficients:

```{r}
ggplot(outcomes, aes(x=V1,y=V2))+geom_point() + facet_wrap(~pearson)
```





| Correlation | Strength | Direction |
|:--|:--|:--|
| $-1$ to $-0.9$ | Very Strong | Negative | 
| $-0.9$ to $-0.7$ | Strong | Negative | 
| $-0.7$ to $-0.4$ | Moderate | Negative | 
| $-0.4$ to $-0.2$ | Weak | Negative | 
| $-0.2$ to $0$ | Negligible | Negative | 
| $0$ to $0.2$ | Negligible | Positive | 
| $0.2$ to $0.4$ | Weak | Positive | 
| $0.4$ to $0.7$ | Moderate | Positive | 
| $0.7$ to $0.9$ | Strong | Positive | 
| $0.9$ to $1$ | Very Strong | Positive |

### Caution

+ Use caution when interpreting a pearson correlation coefficient.
+ The correlation may not tell you what you think it does about the data.

Consider the following data set:
```{r}
cor(anscombe$x1,anscombe$y1)
```

+ Based on the correlation coefficient we might imagine a scatter plot with a slight positive linear association. 
+ We would be correct!

```{r}
ggplot(anscombe, aes(x=x1,y=y1))+geom_point()
```

Now let's check
```{r}
cor(anscombe$x2,anscombe$y2)
```

+ The same correlation coefficient! We should get a similar graph right?

```{r}
ggplot(anscombe, aes(x=x2,y=y2))+geom_point()
```

+ Nope, what about the others?
```{r}
cor(anscombe$x3,anscombe$y3)

cor(anscombe$x4,anscombe$y4)
```


```{r}
ggplot(anscombe, aes(x=x3,y=y3))+geom_point()
ggplot(anscombe, aes(x=x4,y=y4))+geom_point()
```

---

### Shortcomings and Alternatives

+ You should always make a scatter plot before using the pearson correlation coefficient to conclude any thing about the shape of your data.
+ The Pearson correlation coefficient measures how close the data is to fitting on a specific line.
+ It is looking for a **linear** relationship. 

## Class Activity

1. Make a scatter plot for penguin body mass vs. flipper length with facets by species. Looking only at the plots, can you tell for which species the body mass has the strongest relationship to flipper length? What about the weakest?

```{r}

```



2. Use the `filter()` and `cor()` function to find the Pearson correlation coefficient for body mass and flipper length for each species. Which species has the strongest relationship?


```{r}

```

