---
title: "Class Activity 9"
output:
  pdf_document:
    toc: yes
  html_document:
    css: ./style.css
    toc: no
    toc_float: yes
    theme: cosmo
editor_options:
  chunk_output_type: console
---
  
```{r global_options, include = FALSE}
library(knitr)
knitr::opts_chunk$set(eval = TRUE, results = TRUE)
```


1. Suppose a population unkown population mean and population standard deviation $2.5$. A sample of $450$ observations has a sample mean of $\bar{x}=62$. Find a $95 \%$ confidence interval.

```{r}

```

2. What are the $z$-scores corresponding to a $70 \%$ confidence level?

```{r}

```

3. Suppose average pizza delivery times are normally distributed with an unknown population mean and a population standard deviation of six minutes. A random sample of $28$ pizza delivery restaurants is taken and has a sample mean delivery time of $36$ minutes. Find a $90 \%$ confidence interval for the population mean delivery time.

```{r}

```

4. From a population with population mean $16$ and standard deviation $2$ a sample of $35$ observations is taken. Provide an interval such that there is an $80 %$ chance that the sample mean falls within the range.

```{r}

```

5. Suppose scores on exams in statistics are normally distributed with an unknown population mean and a population standard deviation of $3$ points. A random sample of $36$ scores is taken with an mean score of $72$. Find a $98 \%$ confidence interval for the mean exam score of the population.

```{r}

```
