---
title: "CA 22: Linear Regression"
output:
  html_document:
    css: ./style.css
    toc: yes
    toc_float: yes
    theme: cosmo
  pdf_document:
    toc: yes
editor_options:
  chunk_output_type: console
---




```{r global_options, include = FALSE}
library(knitr)
library(tidyverse)
library(car)
library(rgl)
library(palmerpenguins)
knitr::opts_chunk$set(eval = TRUE, results = TRUE)
```


```{r}
penguins <- na.omit(penguins)
```

---

## Linear Regression
```{r}
load("~/MAT104-Fall2024/Week12/parenthood.Rdata")
```

Let's go back to the parenthood data we used last class:

```{r}
ggplot(parenthood, aes(x=dan.sleep,y=dan.grump))+geom_point()
```

The data looks like there is a linear relationship between `dan.sleep` and `dan.grump`, so let's add a line to our plot that represents this relationship.

### Meaning of the Parameters

To make an equation for a line we use the slope-intercept formula:

$$y=mx+b$$
where $m$ is the slope of the line and $b$ is the $y$-intercept. 

In statistics, we typically use different letters but the equation is the same:
$$\hat{Y_i} = b_1 X_i + b_0$$
where $b_1$ is the slope and $b_0$ is the $y$-intercept. The values $b_1$ and $b_0$ are called coefficients. 

1. Interpret $b_1$, $b_0$, $X_i$, and $\hat{Y}_i$ in the context of the parenthood data. Make a best guess for $b_0$ and $b_1$. (We guessed $b_0 = 135$ and $b_1 = -10$ last class already but have not yet interpreted their meanings). 



Let's add the line we predicted to the graph

```{r}
ggplot(parenthood, aes(x=dan.sleep,y=dan.grump)) +
  geom_point() + 
  geom_abline(intercept = 135, slope = -10, color="blue") 
```


### Residuals

+ We can do better than estimating by eye though. 
+ We should choose the line that minimize the error in our predictions.

The graph below displays the error between our prediction and the true data in red:

```{r, eval=FALSE}
# Use our slope and intercept guesses to predict the y-values


# Plot segments joining the actual points and the predicted points
ggplot(parenthood, aes(x=dan.sleep,y=dan.grump)) +
  geom_point() + 
  geom_abline(intercept = 135, slope = -10, color="blue") + 
  geom_segment(aes(xend = dan.sleep, yend = predictions$Y_hat, color = "residual"))
```

To lengths of these little red segments are called **residuals**. We can find how big the residuals are by finding the difference between the predicted value and the actual value:

$$\epsilon_i = Y_i - \hat{Y}_i$$

2. Calculate the residual corresponding to the first day, $\epsilon_1$. 

```{r}

```

+ the residual is negative when our prediction is an overestimate
+ the residual is positive when our prediction is an underestimate.

Putting these ideas together, we can see that our real data is equal to our prediction plus the residuals:

$$Y_i = \hat{Y}_i + \epsilon_i = b_1X_i + b_0 + \epsilon_i$$

---

## Minimizing error


+ One approach for this is to minimize the so called **sum of the squared residuals**:

$$ \sum \epsilon_i^2 = \sum (Y_i - \hat{Y}_i)^2$$

---

### Using R to find the fits


## Multiple Regression


The model we use for two predictors is:
$$\hat{Y}_i = b_2 X_{i,2} + b_1 X_{i,1} + b_0$$

where $X_{i,2}$ is the amount of sleep the baby got on day $i$ and $X_{i,1}$ is the amount of sleep Danielle got on day $i$.

+ If we had three predictors the equation would be:
$$\hat{Y}_i = b_3 X_{i,3} + b_2 X_{i,2} + b_1 X_{i,1} + b_0$$


To find the best fitting regression line we use `lm()`:

```{r,eval=FALSE}
scatter3d(dan.grump ~ dan.sleep + baby.sleep, parenthood)
rglwidget()
```

3. Find the residual corresponding to the first day using this new model with two predictors.

---

## Class Activity

4. Using the penguins data set, perform a simple linear regression to model body mass using the predictor variable bill length. What values do you get for $\hat{b}_0$ and $\hat{b}_1$? Graph a scatter plot for the data and include your regression model in the plot.

```{r}

```



$\hat{b}_0 = $

$\hat{b}_1 = $



5. Find the sum of the square residuals for the model in exercise 1.


6. Use `cor()` to find the strength of the correlation between bill length and body mass. 


```{r}

```



7. Use simple linear regression to model the relationship between flipper length and body mass for the penguin data. What values do you get for $\hat{b}_0$ and $\hat{b}_1$? Plot a scatter plot for the data with the line you found.

```{r}

```



8. Use multiple linear regression to model the body mass using the predictors flipper length and bill length for the penguin data. Assuming $X_1$ is flipper length and $X_2$ is bill length, what values do you get for $\hat{b}_0$,  $\hat{b}_1$, and $\hat{b}_2$? 

```{r}

```



