---
title: "Class Activity 1"
output:
  pdf_document:
    toc: yes
  html_document:
    css: ./style.css
    toc: no
    toc_float: yes
    theme: cosmo
editor_options:
  chunk_output_type: console
---
  
```{r global_options, include = FALSE}
library(knitr)
knitr::opts_chunk$set(eval = TRUE, results = TRUE)
```

When you are finished with the assignment, "knit" (above this in the middle) to pdf and submit to gradescope (the course code is: RKX44J)

1. In the space below create a variable called that saves the value 15 to a variable called `a`.

```{r}
# delete this and instead write your answer here
```

2. Create a new code chunk below and type code that will find raise `a` to the 10th power.



3. Now review the code chunk below. It lists the calories for the meals I ate yesterday and then adds up my calories for the day. In the empty code chunk write code that will save a list called `scores` with the values `25,65,33` and find the sum of those values. 

```{r}
calories <- c(550,920,1000)
sum(calories)
```

```{r}
# delete this and instead write your answer here
```
