---
title: "Day24_Notes : Difference in means"
output:
  html_document:
    css: ./style.css
    toc: yes
    toc_float: yes
    theme: cosmo
  pdf_document:
    toc: yes
editor_options:
  chunk_output_type: console
---
  
```{r global_options, include = FALSE}
library(knitr)
library(tidyverse)
library(openintro)
knitr::opts_chunk$set(eval = TRUE, results = TRUE)
```

---
  
## Today's Agenda

- Review
- Two Means

---

1. Pew Research asked a random sample of $1000$ American adults whether they supported the increased usage of coal to produce energy. Their sample showed that $46 \%$ of support increased coal usage. Set up hypotheses to evaluate whether a majority of American adults support or oppose the increased usage of coal.

$H_0:$ 

$H_A:$ 

```{r}

```

2. You are given the following hypotheses:

$H_0: \mu = 60$

$H_A: \mu \neq 60$

We know that the population standard deviation is $8$ and the sample size is $20$. For what sample mean(s) would the $p$-value be equal to $0.05$? 

3. You are given the following hypotheses:

$H_0: \mu = 60$

$H_A: \mu \neq 60$

We know that the sample standard deviation is $8$ and the sample size is $20$. For what sample mean(s) would the $p$-value be equal to $0.05$? 

---

## Difference of means in groups

4. A scientific experiment measured change in blood pressure due to a medication in a control and treatment group. In their measurements negative data indicates a decrease in blood pressure. The control group had an average decrease of $-1.4$ and the treatment group had an average decrease of $-4$. With $9$ people in each group and sample standard deviations $5.2$ and $2.4$ in the control and treatment respectively, does this data provide statistically significant evidence of the effectiveness of the medication?

### Difference of means SE

For difference of means we use:

$$SE = \sqrt{\frac{(\sigma_1)^2}{n_1} + \frac{(\sigma_2)^2}{n_2}}$$
