---
title: "Class Activity 3"
output:
  html_document:
    css: ./style.css
    toc: no
    toc_float: yes
    theme: cosmo
  pdf_document:
    toc: yes
editor_options:
  chunk_output_type: console
---
  
```{r global_options, include = FALSE}
library(knitr)
knitr::opts_chunk$set(eval = TRUE, results = TRUE)
```



1. Load the `openintro` package locally using the `library()` function. (You *may* need to install the package first)

```{r}
# code to load the package

```

2. Inside this package is a dataset called `yrbss` full of data about high school students. Choose a an appropriate name and save this data frame to your local environment.

```{r}
# saving data frame to environment

```

3. Choose an appropriate name to save the height column from the `yrbss` data to your local environment and remove all missing values.

```{r}
# remove missing values from height and saving it to environment

```



4. Find the 25th, 50th, 75th percentiles for the height data

```{r}
# finding quartiles for the data

```

5. Now use a logic operator to save all data points with a height less than or equal to $1.60$ to your local environment. 

```{r}
# saving heights less than or equal to 1.60

```

6. Divide the number of data points with height less than or eual to 1.60 by the total number of data points to verify that it is approximately 25%.

```{r}
# verify 25th percentile

```


7. Finally, plot a boxplot by using the function `boxplot( height)`. Approximately how tall/short does a student need to be to be considered an outlier?

```{r}
# code for boxplot

```

Type your answer here
