---
title: "Class Activity 7"
output:
  html_document:
    css: ./style.css
    toc: no
    toc_float: yes
    theme: cosmo
  pdf_document:
    toc: yes
editor_options:
  chunk_output_type: console
---
  
```{r global_options, include = FALSE}
library(knitr)
knitr::opts_chunk$set(eval = TRUE, results = TRUE)
```


1. Plot the probability distribution described by a loaded six-sided die that is twice as likely to land on $6$ than any other value (all other values have equal probability).

```{r}
# finding quartiles for the data

```

2. Find the expected value of the die roll from above.

```{r}
# finding quartiles for the data

```

3. A portfolio’s value increases by $16 \%$ during a financial boom and by $8 \%$ during normal times. It decreases by $12 \%$ during a recession. What is the expected percent return on this portfolio if each scenario is equally likely?

```{r}
# code to compute expected return

```

4. What is the standard deviation of the expected return?

```{r}
# saving data frame to environment

```

5. Consider the following card game with a well-shuffled deck of cards. If you draw a red card ($26/52$ cards are red), you win nothing. If you draw a spade ($13/52$ cards are spades), you win $\$5$. For any club ($13/52$ cards are clubs), you win $\$10$ plus an extra $\$20$ for the ace of clubs. (A) Find the expected winnings for a single game and the standard deviation of the winnings. (B) If it costs $\$6$ to play the game, is it in your benefit to play?

```{r}
# (a) code to find the expected winnings

# (b) Should you play the game?

```

