---
title: "Lab 2 - Conditional Probability"
author: Student 1 Name, Student 2 Name
output:
  html_document:
    css: ./style.css
    toc: no
    toc_float: no
    theme: cosmo
  pdf_document:
    toc: yes
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(openintro)
library(tidyverse)
set.seed(123)
```

## Instructions

In this lab, you will investigate data and give an explanation of how rare the data is given our expectations. 

---


Your investigation will focus on the performance of one player: Kobe Bryant of the Los Angeles Lakers. His performance against the Orlando Magic in the 2009 NBA Finals earned him the title Most Valuable Player and many spectators commented on how he appeared to show a hot hand. Having a *hot hand* means that Kobe would tend to go on shooting streaks where he would make lots of shots in a row. You will investigate this belief and make a determination about whether you believe Kobe exhibited the hot hand phenomenon in this game. The data file we’ll use is called `kobe_basket` and is part of the openintro library. 

1. Save the `kobe_basket` dataset from the `openintro` package locally. Open the data set from your environment and take a look at it.

```{r}
#insert code here
```

In this data frame, every row records a shot taken by Kobe Bryant. If he hit the shot (made a basket), a hit, H, is recorded in the column named shot, otherwise a miss, M, is recorded.

Just looking at the string of hits and misses, it can be difficult to gauge whether or not it seems like Kobe was shooting with a hot hand. One way we can approach this is by considering the belief that *hot hand* shooters tend to go on shooting streaks. For this lab, **we define the length of a shooting streak to be the number of consecutive baskets made until a miss occurs**.

For example, in Game 1 Kobe had the following sequence of hits and misses from his nine shot attempts in the first quarter:

$$ H \ M \ | \ M \ | \ H \ H \ M \ | \ M \ | \ M \ | \ M $$

2. What does the symbol "|" represent in the sequence of hits and misses? 



3. Insert code that will display the first nine shots in the data frame in order to verify the above sequence. 

```{r}
#insert code here
```



4. What does a streak length of 1 mean, i.e. how many hits and misses are in a streak of 1? What about a streak length of 0? 

5. Counting streak lengths manually for all $133$ shots would get tedious, so we’ll use a custom function `calc_streak` to calculate them. Call the function `calc_streak()` and plug in the shot column from the data frame. Save the result locally in a vector called `length`.

```{r}
#insert code here
```

6. Create a bar graph displaying `length`. (You may want to look at class activity 2 to see how to do this) 

```{r}
#insert code here
```

<div>
:::{#answer}

ANSWER HERE

:::
</div> 

7. Describe the distribution of shot streak lengths. 


8. What is Kobe's average streak length, save this locally as `kobe_avg_streak`? 

```{r}
#insert code here
```

9. What is Kobe's largest streak length?


---

##### Compared to What?

We’ve seen that Kobe had some long shooting streaks, but are they long enough to support the belief that he had a hot hand? What can we compare them to?

To answer these questions, let’s return to the idea of independence. Two processes are independent if the outcome of one process doesn’t affect the outcome of the second. If each shot that a player takes is an independent process, having made or missed your first shot will not affect the probability that you will make or miss your second shot.

A shooter with a hot hand will have shots that are not independent of one another. Specifically, if the shooter makes their first shot, the hot hand model says they will have a higher probability of making their second shot.

Let’s suppose for a moment that the hot hand model is valid for Kobe. During his career, the percentage of time Kobe makes a basket (i.e. his shooting percentage) is about $45 \%$. That is, if $H$ represents a made shot, then in probability notation,


$$P(\text{ H }) = 0.45$$

If he makes the first shot and has a hot hand (i.e. we are assuming the shots are *not* independent), then the probability that he makes his second shot would go up to, let’s say to $60 \%$,

$$P(\text{second shot is }H | \text{first shot is } H) = 0.60$$.

On the other hand, if the second shot is **independent** of the first shot then we would expect

$$P(\text{second shot is }H | \text{first shot is } H) = 0.45$$.

This would mean that the second shot is **unaffected** by the first shot. This is exactly our definition of what it means for two events to be independent. 

10. Suppose event that for two events $A$ and $B$ we know that $P(A) = .3$ and $P(B) = .4$. Suppose $A$ and $B$ are independent events and compute $P(A|B)$ and $P(B|A)$


---

Now that we’ve phrased the situation in terms of independent shots, let’s return to the question: how do we tell if Kobe’s shooting streaks are long enough to indicate that he has a hot hand?

We will simulate a basketball player in `R`. The special thing about our simulation is that we *know* the player *does not* have a hot hand. We will set it up so that every shot is independent of every other shot. Then we can run the simulation and compare that to Kobe's performance. 

##### More Simulations in R

Simulating independent events repeated over and over is very easy to do in `R`. For example, you can simulate flipping a fair coin with the following:

```{r}
coin_outcomes <- c("heads", "tails")

sample(coin_outcomes, size = 1, replace = TRUE)
```

The vector `coin_outcomes` can be thought of as a hat with two slips of paper in it: one slip says `heads` and the other says `tails`. The function `sample` draws one slip from the hat and tells us if it was a head or a tail (the `replace = TRUE` argument indicates we put the slip of paper back in the hat before drawing again).

If you wanted to simulate flipping a fair coin 100 times, you could either run the function 100 times or, more simply, adjust the `size` argument, which governs how many samples to draw and save the resulting vector of heads and tails in a new object called `sim_fair_coin`.

```{r}
sim_fair_coin <- sample(coin_outcomes, size = 100, replace = TRUE)
```

To view the results of this simulation, type the name of the object and then use `table` to count up the number of heads and tails.

```{r}
sim_fair_coin

table(sim_fair_coin)
```

Not all coins are fair and we often encounter situations where the outcomes aren't equally likely. The `sample()` function treats each outcome equally by default, but we can adjust that. Say we’re trying to simulate an unfair coin that we know only lands heads $20 \%$ of the time. We can adjust for this by adding an argument called prob, which provides a vector of two probability weights.

```{r}
sim_unfair_coin <- sample(coin_outcomes, size = 100, replace = TRUE, prob = c(0.2, 0.8))
```

The `prob=c(0.2, 0.8)` indicates that for the two elements in the `outcomes` vector, we want to select the first one, `heads`, with probability $0.2$ and the second one, `tails` with probability $0.8$. Another way of thinking about this is to think of the outcome space as a bag of 10 chips, where 2 chips are labeled “head” and 8 chips “tail”. Therefore at each draw, the probability of drawing a chip that says “head” is $20 \%$, and “tail” is $80 \%$.

---




11. Run the simulation of flipping the unfair coin 100 times, how many flips came up heads? How many heads should you expect from this unfair coin? 

12. If your simulation were not as close to the expectation as you wanted, what could you change about the simulation to get closer to the expectation?


---

##### Simulating the Independent Player

Simulating a basketball player who has independent shots uses the same mechanism that you used to simulate a coin flip. We will use `R` to make a *robot* basket ball player with the exact same shooting percentage as Kobe. Then we will ask the robot to shoot 133 baskets and compare the results to Kobe's results. We **know** that the robot **does not** have a hot hand, so Kobe should perform better than the robot if he does have a hot hand.

13. Make a vector called `shot_outcomes` that represent the possible outcomes from shooting a basketball.

```{r}
#insert code here
```

14. Use the `sample()` function to simulate $133$ shots from a shooter with a shooting percentage of $45 \%$. Assign the output of this simulation to a new object called `sim_basket`.

```{r}
#insert code here
```


---


15. Using `calc_streak()`, compute the streak lengths of `sim_basket`, and save the results in a data frame called `sim_streak`.

```{r}
#insert code here
```

16. Plot a bar graph for the streak lengths of the simulated player.

```{r}
#insert code here
```

16. Describe the distribution of streak lengths. 

17. What is the average streak length for this simulated player with a $45 \%$ shooting percentage? 

```{r}
#insert code here
```

18. How long is the player’s longest streak of baskets in $133$ shots?


19. If you were to run the simulation of the player a second time, how would you expect its streak distribution to compare to the distribution from the question above? Exactly the same? Somewhat similar? Totally different? Explain your reasoning.



20. What conclusions have you made about Kobe and the hot hand phenomenon? Use what you've observed in this lab in order to justify your answer.

