---
title: "CA 14 : Hypothesis Testing II"
output:
  html_document:
    css: ./style.css
    toc: yes
    toc_float: yes
    theme: cosmo
  pdf_document:
    toc: yes
editor_options:
  chunk_output_type: console
---
  
```{r global_options, include = FALSE}
library(knitr)
library(tidyverse)
library(openintro)
knitr::opts_chunk$set(eval = TRUE, results = TRUE)
```

---
  
## Today's Agenda

- Two Sided Test
- Practice

---


## Two sided

---

1. Some people claim that they can tell the difference between a diet soda and a regular soda in the first sip. A researcher wanting to test this claim randomly sampled $80$ such people. He then filled $80$ plain white cups with soda, half diet and half regular through random assignment, and asked each person to take one sip from their cup and identify the soda as diet or regular. $53$ participants correctly identified the soda. Does this data provide strong evidence that people can tell the difference between regular and diet soda? (when a significance level is not specified use $\alpha=.05$).

$H_0:$ 

$H_A:$ 


```{r}

```

---

2. It is believed that $40 \%$ of people pass their driving test on the first attempt. Suppose you think the percentage is different than $40 \%$. So, you perform a hypothesis test and sample $100$ people. Of the sampled people, $43$ reply that they passed on their first attempt. Set up a hypothesis test and make a conclusion with a $10 \%$ significance level.

$H_0:$ 

$H_A:$ 

```{r}

```

3. A child is seeing how long they can hold their breathe under water. The child thinks they can hold their breathe for $150$ seconds on average. The child’s dad thinks it less than that. He samples his daughter holding her breathe eight times and the results are $144$, $152$, $138$, $144$, $136$, $162$, $158$, and $142$. From the perspective of the dad, perform a hypothesis test using a $5 \%$ level of significance. Does the data provide sufficient evidence to reject the null hypothesis?

$H_0:$ 

$H_A:$ 

```{r}

```

4. Pew Research asked a random sample of $1000$ American adults whether they supported the increased usage of coal to produce energy. Their sample showed that $46 \%$ of support increased coal usage. Set up hypotheses to evaluate whether a majority of American adults support or oppose the increased usage of coal.

$H_0:$ 

$H_A:$ 

```{r}

```

5. You are given the following hypotheses:

$H_0: \mu = 60$

$H_A: \mu \neq 60$

We know that the sample standard deviation is $8$ and the sample size is $20$. For what sample mean would the $p$-value be equal to $0.05$? 
